---
title: "RAPS Package Creation"
subtitle: "R Aid for P Systems"
author: "Xopre"
date: "`r format(Sys.time(), '%d de %B de %Y')`"
output: 
  html_document:
    toc: true # Table of Contents
    toc_float: 
      collapsed: true # Flotante a la iqzda, colapsada por defecto
    number_sections: false # Para numerar las secciones
    df_print: kable # Data frame printing
    theme: readable # El tema de Bootstrap para el texto # https://bootswatch.com/3/ (cerulean, cosmo y flatly son otras buenas opciones)
    highlight: default # Para los bloques sintácticos (R)
    # Referencia: https://bookdown.org/yihui/rmarkdown/html-document.html
codification: "UTF-8"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo = FALSE}
.blackbox {
  padding: 1em;
  background: #F47174;
  color: white;
  /* border: 2px solid orange; */
  border-radius: 10px;
}
.greenbox {
  padding: 1em;
  background: #79d279;
  color: white;
  /* border: 2px solid orange; */
  border-radius: 10px;
}
.center {
  text-align: center;
}

.code {
  font-family: Courier, "Lucida Console", monospace;
}
```

# Updating R if necessary
```{r}
# install.packages("installr")
# library(installr)
# updateR()
```


# RAPS
[Reference](https://tinyheero.github.io/jekyll/update/2015/07/26/making-your-first-R-package.html)       

Basic packages needed:
```{r}
# install.packages("devtools") # To make packages
# install.packages("roxygen2") # For documentation
```

Creating the framework (run only once!):
```{r}
# setwd("~/GitHub/master21/Beca colab/RAPS") # Delete if useless
# my_path = getwd()

# devtools::create(path = my_path) # Create framework (last component used as package name)
```

Folders:
1. DESCRIPTION: https://r-pkgs.org/description.html
2. RAPS.Rproj: Project to combine everything
3. NAMESPACE: There's no need of editing this
4. R folder, with all the functions


To update everytime a change occurs:
```{r}
# devtools::document() # To update
# devtools::install() # To install as package locally

# Guides about roxygen2's tags (@param and so on):
# https://r-pkgs.org/man.html
# https://roxygen2.r-lib.org/articles/rd.html
```
If you get an `lazy-load database ... RAPS.rdb is corrupt` then restart R session.

About functions in the R folder:
- Never use "library" in them

## TODO:
- Add basic data (transition.xml)
