---
title: "Workflow in RAPS"
subtitle: "RAPS: R Aid for P Systems"
author: "Xopre"
date: "`r format(Sys.time(), '%d de %B de %Y')`"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: true
    number_sections: false 
    df_print: kable
    theme: readable
    highlight: default 
codification: "UTF-8"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo = FALSE}
.blackbox {
  padding: 1em;
  background: #F47174;
  color: white;
  /* border: 2px solid orange; */
  border-radius: 10px;
}
.greenbox {
  padding: 1em;
  background: #79d279;
  color: white;
  /* border: 2px solid orange; */
  border-radius: 10px;
}
.center {
  text-align: center;
}

.code {
  font-family: Courier, "Lucida Console", monospace;
}
```

If RAPS is not installed, uncomment the following:
```{r}
# devtools::document() # To update the documentation
# devtools::install() # To install as package
## Or use:
# devtools::install_github("Xopre/RAPS")
```

```{r}
library(RAPS)
```


As shown by the diagram in the [quickstart section](https://github.com/Xopre/RAPS#quickstart), first of all we will need a URL and, in this scenario, the [`psystems-examples`](https://github.com/Xopre/psystems-examples) repository comes handy, with some examples of P systems, processed with P-Lingua 5.0, between other tools:

```{r}
my_url = "https://raw.githubusercontent.com/Xopre/psystems-examples/main/plingua5/transition_1.xml"
```

Now we can extract the P system inside the URL, with the `url2rap()` function, which creates a `rap` (*Representating A P-system*) variable. In order to show the `rap`, we have the `show_rap()` function.

```{r}
# my_rap = RAPS::url2rap(my_url)
my_rap = RAPS::path2rap(demo = TRUE) # We can even call it without a url
RAPS::show_rap(my_rap)
```

However, what is a P system which can't evolve? To make the P system evolve we have the following functions:
* `choose_rule(rap)`
* `apply_rule(rap, rule_id)`
* `simulate(rap, n_steps)`
* `simulate_one = simulate(n_steps = 1)`

Let's give them a try:

```{r}
my_new_rap = RAPS::simulate_one(my_rap)
RAPS::show_rap(my_new_rap)
```

And now let's see what would happen if we simulate 100 steps:
```{r}
my_newer_rap = RAPS::simulate(my_rap, n_steps = 100)
RAPS::show_rap(my_newer_rap)
```
